Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-12 tex/paper1/paper1.tex
edits to the paper

\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
The first contribution to both models $P_{0}$ and $P_{i}$ is a
\PL-like \PS.  It is present in both wavebands studied and in all the
regions, and so parsimony suggests that the mechanism of its creation
is both similar and ubiquitous in all parts of the solar atmosphere.
We hypothesize that the \PL\ \PS\ is due to the sum of a distribution
of a large number of emission events having different amounts of
emission. \cite{2011soca.book.....A} describes how a \PL\ \PS\ may
obtained from such a distribution, and that argument is outlined
below.

@@

Future studies will include examining power spectra at many more
locations on and off the disk, as well as using the AIA 355\AA, 94\AA,
131\AA and 211\AA\ wavebands.  The power-law index in individual
pixels will also be determined, and correlated with other physical
quantiies such as the emission from those pixels.  Finally, a better
understanding of the source of the power-law power spectrum will come
from comparing the \Fps\ of simulated observations to the \Fps\ of the
data in all the AIA wave-bands that are sensitive to higher
temperatures.  This will bring new constraints on the simulations and
improve our understanding of the temporal behavior of the solar
corona.

@@

Hence, the number of effectively independent pixels time-series must
be calculated.  First, a pair of randomly chosen next-nearest neighbor
pixels are selected from the region.  Next nearest neighbor pixels are
chosen as close physical proximity is most likely to express the
strongest interdependence.  Next, the cross correlation $c(\tau)$
function between two randomly chosen next-nearest neighbor pixels is
calculated.  The cross correlation coefficient measures the linear
dependence of two time series $X(t)$ and $Y(t \pm \tau)$ at different
lags $\tau$.  This is used to define a coefficient of independence
between the neighbors,
\begin{equation}
\label{eqn:ind}
\rho = 1 - \max|c(\tau)|.
\end{equation}
When $\rho$ is 1, the cross-correlation coefficient is zero, and there
is no measurable linear dependence between neighboring time series.
When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
the two time-series are linearly dependent on each other.  This
procedure is repeated 10,000 and the mean value $\hat{\rho}$ is
calculated. The effective number of independent pixels in region is
given by
\begin{equation}
\label{eqn:nind}
N_{eff}= 1 + \hat{\rho}(N_{pixel}-1).
\end{equation}
The number of independent measurements $N$ is set to $N_{eff}$ in
Equation \ref{eqn:sigmamean}.

Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.
The frequency $\nu$ is defined as $f/f_{0}$ where $f$ is the FFT
frequency in Hz, and $f_{0}$ is the lowest non-zero FFT frequency
defined by the data (Section \ref{sec:obs}).

\subsection{Model fitting}

A three step fitting process is used to fit Models 1 and 2 to the
data.
\begin{enumerate}
\item Model 1 is fit to the data using the distribution widths
  $\sigma$.  Since this is much wider than the standard error in
  the mean, it allows the fitting algorithm to converge to an
  approximate fit solution.
\item The estimated values to the model parameters are then used as
  initial guesses to the second fit of Model 1, assuming the much
  narrower estimated error $\sigma/\sqrt{N_{eff}}$.  This generates
  a better estimate to the parameters of the model fit.
\item The residuals of the model 1 fit to the data are then used to
  estimate the model parameters of $G(\nu)$.
\item Model 2 is fit to the data using the distribution widths
  $\sigma_{d}$, seeded with the maximum likelihood parameter values
  from Step 2 and the estimated $G(\nu)$ model parameters from Step 3.
\item Model 2 is fit to the data using the maximum likelihood model
  parameter values at Step 4 and the adjusted widths
  $\sigma_{d}/\sqrt{N}{ind}$.
\end{enumerate}

@@

\bibliography{references}
\end{document}
However, other more complex models are certainly possible.  For
example, \cite{1993ASPC...42..111H} modelled the background
chromospheric Fourier \PS\ of a series of Ca-II K-line
images using a 19-parameter fit consisting of a constant background,
three components of the form
\begin{equation}
\label{eqn:harvey1}
P(\nu) \propto \frac{1}{1 + (2\pi \nu T_{0})^{b}}.
\end{equation}
and two components of the form
\begin{equation}
\label{eqn:harvey2}
P(\nu) \propto
\left(
\frac{\nu}{\nu_{0}}
\right)^{c}
\left(
\frac{\Gamma^{2}}{(\nu-\nu_{0})^{2} + \Gamma^{2}}
\right)^{b}.
\end{equation}

@@

>>>>

\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}

The first contribution to both models $P_{0}$ and $P_{i}$ is a
\PL-like \PS.  It is present in both wavebands studied and in all the
regions, and so parsimony suggests that the mechanism of its creation
is both similar and ubiquitous in all parts of the solar atmosphere.
We hypothesize that the \PL\ \PS\ is due to the sum of a distribution
of a large number of emission events having different amounts of
emission. \cite{2011soca.book.....A} describes how a \PL\ \PS\ may
obtained from such a distribution, and that argument is outlined
below.

@@

Future studies will include examining power spectra at many more
locations on and off the disk, as well as using the AIA 355\AA, 94\AA,
131\AA and 211\AA\ wavebands.  The power-law index in individual
pixels will also be determined, and correlated with other physical
quantities such as the emission from those pixels.  Finally, a better
understanding of the source of the power-law power spectrum will come
from comparing the \Fps\ of simulated observations to the \Fps\ of the
data in all the AIA wave-bands that are sensitive to higher
temperatures.  This will bring new constraints on the simulations and
improve our understanding of the temporal behavior of the solar
corona.

@@

Hence, the number of effectively independent pixels time-series must
be calculated.  First, a pair of randomly chosen next-nearest neighbor
pixels are selected from the region.  Next nearest neighbor pixels are
chosen as close physical proximity is most likely to express the
strongest interdependence.  Next, the cross correlation $c(\tau)$
function between two randomly chosen next-nearest neighbor pixels is
calculated.  The cross correlation coefficient measures the linear
dependence of two time series $X(t)$ and $Y(t \pm \tau)$ at different
lags $\tau$.  This is used to define a coefficient of independence
between the neighbors,
\begin{equation}
\label{eqn:ind}
\rho = 1 - \max|c(\tau)|.
\end{equation}
When $\rho$ is 1, the cross-correlation coefficient is zero, and there
is no measurable linear dependence between neighboring time series.
When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
the two time-series are linearly dependent on each other.  This
procedure is repeated 10,000 times and the mean value $\hat{\rho}$ is
calculated. The effective number of independent pixels in region is
given by
\begin{equation}
\label{eqn:nind}
N_{eff}= 1 + \hat{\rho}(N_{pixel}-1).
\end{equation}
The number of independent measurements $N$ is set to $N_{eff}$ in
Equation \ref{eqn:sigmamean}.  The value $\sigma_{mean}$ is used as
the estimate of the error in the \FPs.  Table \ref{tab:neff} shows the
number of pixels in the region and the estimated number of effective
pixels.

\subsection{Model fitting and selection}

The \FPs\ are assumed to be normally distributed with a width given by
$\sigma_{mean}$ as calculated above.
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.
The frequency $\nu$ is defined as $f/f_{0}$ where $f$ is the FFT
frequency in Hz, and $f_{0}$ is the lowest non-zero FFT frequency
defined by the data (Section \ref{sec:obs}).  A five step fitting
process is used to fit Models 1 and 2 to the data.  Maximum likelihood
estimates are found using scipy's maximum likelihood estimators

\begin{enumerate}
\item Maximum likelihood estimates to the values of the parameters of
  Model 1 are found using the distribution widths $\sigma$.  Since
  these widths are much larger than $\sigma_{mean}$ is much wider than
  the standard error in the mean, it allows the fitting algorithm to
  converge to an approximate fit solution.
\item The estimated values to the Model 1 parameters are then used as
  initial guesses to the second estimate of the Model 1
  parameters. Maximum likelihood estimates to the values of the
  parameters of Model 1 are found using the distribution widths
  $\sigma_{mean}$, seeded with estimated parameter values from step 1.
  This generates a better estimate to the parameters of the model
  fit.  The resulting parameter estimates are the final estimates for
  Model 1.
\item The residuals of the model 1 fit to the data are then used to
  estimate the model parameters of $G(\nu)$.
\item Model 2 is fit to the data using the distribution widths
  $\sigma$, seeded with the maximum likelihood parameter values of
  Model 1 from step 2 and the estimated $G(\nu)$ model parameters from
  step 3.
\item Model 2 is fit to the data using the maximum likelihood Model 2
  parameter values at Step 4 and the widths $\sigma_{mean}$.  The
  resulting parameter estimates are the final estimates for Model 2.
\end{enumerate}

Models are selected using the Akaike and Bayesian Information Criteria
\cite{???} calculated using the final parameter estimates of Models 1
and 2.

@@

\bibliography{references}
\end{document}

However, other more complex models are certainly possible.  For
example, \cite{1993ASPC...42..111H} modelled the background
chromospheric Fourier \PS\ of a series of Ca-II K-line
images using a 19-parameter fit consisting of a constant background,
three components of the form
\begin{equation}
\label{eqn:harvey1}
P(\nu) \propto \frac{1}{1 + (2\pi \nu T_{0})^{b}}.
\end{equation}
and two components of the form
\begin{equation}
\label{eqn:harvey2}
P(\nu) \propto
\left(
\frac{\nu}{\nu_{0}}
\right)^{c}
\left(
\frac{\Gamma^{2}}{(\nu-\nu_{0})^{2} + \Gamma^{2}}
\right)^{b}.
\end{equation}

@@

The mean power spect
